MITM: Logging a Bluetooth Keyboard

### 2013-03-15 final_paper/paper.tex
Added conclusion and results

\section{Results}

@@

\begin{enumerate}
\item Implement the entire attack. Including the denial-of-service and pairing without the users knowledge.
\item Get Ubertooth and succesfully use it to choose victims without having to have prior knowledge about the victim and the keyboard.
\item Implement the entire attack in a single C/C++ application. This would make testing and debugging much easier to perform. Instead of requiring several seperate tools combined together.
\item Acquire passwords!
\end{enumerate}

\section{Conclusions}

>>>>

\section{Results}
We successfully created a proof of concept implementation that can forward keystrokes from a Bluetooth keyboard through the attacker to a victim machine. The proof of concept currently only works in the ideal conditions.

@@

\begin{enumerate}
\item Implement the entire attack. Including the denial-of-service and pairing without the users knowledge.
\item Get Ubertooth and successfully use it to choose victims without having to have prior knowledge about the victim and the keyboard.
\item Implement the entire attack in a single C/C++ application. This would make testing and debugging much easier to perform. Instead of requiring several separate tools combined together.
\item Acquire passwords!
\end{enumerate}

\section{Conclusions}
Our work shows that a Bluetooth keylogger is possible to do. We successfully forwarded packets from the keyboard to the victim with no delay. Accomplishing this task was easier said than done. We had to use several software packages in the correct order to get the behaviors we wanted. The main conclusion we came away with is that Bluetooth is needlessly complex. The API is horrible and underdeveloped. Which was not explained by any documentation we found. The documentation was useless and led us in the wrong direction 99\% of the time. If anyone could improve Bluetooth in any way we recommend making the API cleaner and standardized and improving the documentation that goes with it.
